Multiple deprivation index using small area estimation methods: an application for the adult population in Colombia

### 2022-02-03 Paper_MPI_CEPAL/main.tex
Preguntas a discutir

Based on the new ``Multiple deprivation index" for Latin American countries produced by the Economic Commission for Latin America and the Caribbean, this paper shows the case study of Colombia to obtain small area estimates. This country counts with a recent population census providing most of the information required to compute the multiple deprivation index in small domains. However, for two indicators the information at unit level is not available, for which different small area estimation methods are implemented. A parametric bootstrap algorithm is used to provide uncertainty measures.

@@

>>>>

Based on the new ``Multiple deprivation index" (MDI) for Latin American countries produced by the Economic Commission for Latin America and the Caribbean, this paper shows the case study of Colombia to obtain estimates of this index in small domains. This country has a recent population census (2018) providing most of the information required to compute the MDI at municipality level. However,  two of the indicators required to compute the index are not available in the census, namely: ``Employment-related income" and ``Lack of social security". Before computing the index, small area estimation (SAE) methods are implemented to obtain unit-level estimates for those specific indicators. Since two different SAE procedures are carried out, a parametric bootstrap algorithm is proposed to provide respective uncertainty measures.

@@

\textcolor{red}{A discutir:}
\begin{itemize}
\item \textcolor{red}{Mencionamos el Índice de CEPAL? qué pasa si enviamos el abstract y el índice no se publica?}
\item \textcolor{red}{Como vamos a llamar estos dos indicadores: ``Employment-related income" y ``Lack of social security"? otras sugerencias?}
\item \textcolor{red}{No mencionar que es un índice solo para adultos ya que falta confirmación- revisar Título}
\item \textcolor{red}{Revisar las keywords}
\item \textcolor{red}{Mencionamos o no el bootstrap?}
\item \textcolor{red}{Orden y credenciales de cada autor}
\end{itemize}
